Lifting CDCL to Relational Domains

### 2016-10-13 contributions.tex
contributions

\section{Contributions}
In this paper, we make the following contributions.
\begin{enumerate}
\item We present a novel program analysis technique that 
lift CDCL algorithm to relational numerical abstract domains.   
Our proposed technique is embodied in our tool called, {\em Titlis}.  
To the best of our knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains.

\item  Experiments on a set of benchmarks drawn from bit-vector 
regression suite in sv-comp, numerical programs and few 
control-intensive benchmarks from hardware domain shows that 
the strict generalization of CDCL algorithm effectively combines 
the efficiency of abstract domains while being path-sensitive and 
bit-precise at the same time.  
\end{enumerate}

>>>>

\paragraph{Contributions}
In this paper, we make the following contributions.
\begin{compactenum}
\item We present a novel program analysis technique that 
lifts the CDCL algorithm to relational numerical abstract domains.   
Our proposed technique is embodied in our tool called, {\em
  Titlis}. \pscmt{It's better not to create a zoo of tool names}  
To the best of our knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains.

\item We present an abstract model search algorithm that strictly 
generalizes the Boolean Constraint Propagation (BCP) procedure to
compute a fixed point over a relational domain.  Our abstract conflict analysis algorithm present a non-trivial 
lifting of the Unique Implication Point (UIP) procedure to relational abstract 
domains in order to learn a generalized reason for conflicts.

\item  Experiments on a set of benchmarks drawn from the bitvector 
category in SV-COMP as well as numerical programs and a few 
control-intensive benchmarks from hardware domain show that 
the strict generalization of CDCL algorithm effectively combines 
the efficiency of abstract domains while being path-sensitive and 
bit-precise at the same time.  
\end{compactenum}
